\documentclass[main.tex]{subfiles} 
\begin{document}
\subsection{Appendix A -  Timeline/Milestones}
\label{sec:A}
\begin{enumerate}
    \item 
\end{enumerate}
\newpage
\subsection{Appendix B - Weekly Status Updates}
\label{sec:B}
\begin{enumerate}[leftmargin=12mm,labelsep=0.1cm]
    \item[] \textbf{\Large \underline{Status \#1 TO Do List - 4/3/2017}}
    
    \begin{enumerate}
         \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
         \begin{enumerate}
            \item We have Babel protocol running on quagga docker in GNS3.
            \item Basic configuration
            \item Captured some initial babel hello packets
         \end{enumerate}
         \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
         \begin{enumerate}
            \item Dig deeper into configuring babel
            \item setup a more complex network and capture babel packets to learn more about the protocol
            \item Test babel's loop avoidance feature.
            \item Configure Babel to use IPv4 rather than IPv6
            \item Explore possibilities of using BABEL in a wireless Mesh network architecture
            \item Limitations to Protocol?
         \end{enumerate}
    \end{enumerate}
    
     \item[] \textbf{\Large \underline{Status \#2 TO Do List - 4/10/2017}}
    \begin{enumerate}
         \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
         \begin{enumerate}
            \item Enable babel routing on a network of quagga routers.
            \item Revamped topology, babeld now running on Ubuntu Server VMs (For updated version of babel)
         \end{enumerate}
         \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
         \begin{enumerate}
            \item Create a hybrid topology that allows gns3 to talk to a wireless client via babel
            \item inject ospf or rip into babel (redistribution)
            \item Break links and see how babel recreate the links. (Ex2)
            \item create a physical topology using routers flashed with open-wrt (Ex3)
            \item Creation of hybrid architecture? Connect GNS3 topology to physical world (Ex4)
            \item Implement BMX6 routing protocol in Physical world? (Ex5)
         \end{enumerate}
    \end{enumerate}
    
     \item[] \textbf{\Large \underline{Dry-Run \#1 TO Do List - 4/17/2017}}
    \begin{enumerate}
         \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
         \begin{enumerate}
            \item Exercises 1, 2, and 3 Instructions are all partially completed
            \item Exercise 4 is defined (Hybrid Network Architecture)
            \item Investigated link re-convergence time when a link is broken and how loop avoidance and load balancing is maintainted. (Ex2)
            \item Have implemented and successfully configured babel on a single access point flashed with Open-wrt. (Ex3)
            \item 
         \end{enumerate}
         \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
         \begin{enumerate}
            \item Finish Report for each of the exercises
            \item Implement Babel between 2 APs flashed with Open-WRT.
            \item Implement Babel in a Hybrid architecture between a Wireless AP and GNS3.
            \item Come up with Exercises 5 and 6.
         \end{enumerate}
    \end{enumerate}
     
     \item[] \textbf{\Large \underline{Dry-Run \#2 TO Do List - 4/24/2017}}
    \begin{enumerate}
         \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
         \begin{enumerate}
            \item test
         \end{enumerate}
         \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
         \begin{enumerate}
            \item test
         \end{enumerate}
    \end{enumerate}
    
\end{enumerate}
\end{document}